% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}
	\project
	{Learning inverse kinematics}{}
	{\website{Shaunfedrick.com/portfolio}{Shaunfedrick.com/portfolio}  }
	{One of the projects I undertook involved addressing the intricate challenges posed by the inverse kinematics problem in robotics, utilizing machine learning techniques. The project was divided into two main phases. The first phase involved training an artificial neural network (ANN) to solve the inverse kinematics problem. The second phase shifted focus to addressing whether given position and orientation data points were feasible within the robot arm's workspace. This was achieved through unsupervised clustering methods, including Gaussian Mixture Models (GMM) and k-means clustering. }
	{python, pytorch,tensorflow, machine learning, robotics,kinematics}
	
	\project		
	{Holonomic Semi autonomous RC Car}{}
	{\website{Shaunfedrick.com/portfolio}{Shaunfedrick.com/portfolio}  }
	{I undertook the development of a Holonomic Semi-autonomous RC Car, a project aimed at creating a versatile robotic vehicle capable of navigating dynamically while performing tasks in a controlled environment. The project incorporated mechanical design, electronics integration, software development, and functional testing to achieve its objectives.}
	{C++, Javascript,Microcontrollers, Controls, Electronics, Rapid prototyping}
	
	\project		
	{6 DOF Path Planning and Control  of Serial linked manipulator}{}
	{\website{Shaunfedrick.com/portfolio}{Shaunfedrick.com/portfolio}  }
	{The project aimed to develop software for a 6dof serial manipulator capable of picking, placing, and manipulating both dynamic and static blocks. The primary challenges included aligning blocks correctly for optimal grip, dealing with block orientations, and developing strategies to topple an opponent's stack.}
	{python,Ros, Gazebo,Kinematics, Dynamics}
	
\end{projects}